\newglossaryentry{plate} {
	name = Plate,
	description = {Rigid, flat body on which a single pedal rests.  The plate is used as a standardizing interface between the main board and a guitar pedal.  There is one plate for each guitar pedal.}
}

\newglossaryentry{pedal} {
	name = Pedal,
	description = {Guitar effects unit used to perform processing on the guitar signal.}
}

\newglossaryentry{foot swtich} {
	name = {Foot Switch},
	description = {Actuation mechanism on each guitar pedal typically used to turn the effect on or off.  The foot switch is built in to the guitar pedal.}
}

\newglossaryentry{main board} {
	name = {Main Board},
	description = {Main unit of the solution containing a number of receivers, the routing circuitry, and the power supply.}
}

\newglossaryentry{receiver} {
	name = {Receiver},
	description = {Receptacle in main board for a plate.  The receiver is designed to make mechanical and electrical connections with an inserted plate, and detect whether or not a plate is currently inserted.}
}

\newglossaryentry{bypass} {
	name = {Bypass},
	description = {In reference to a receiver or plate, the state where the signal is not routed through the electrodes connecting the receiver to the plate.  Instead, the signal is routed directly from the receiver's input to its output.  In some other cases, bypass can refer to the }
}

\newglossaryentry{insert} {
	name = {Insert},
	description = {In reference to a receiver and plate, the act of placing a plate into a receiver slot.}
}

\newglossaryentry{pogo pin} {
	name = {Pogo-Pin}, 
	description = {A spring loaded connector used to make electrical connection between two circuit boards.  The connection is made mechanically by the force of the spring inside a sheath push a plunger upwards towards the mating electrode.  This type of connector can be used for both permenant and temporary connections.}
}